The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Update preprocessing steps

# TODO replace with cleaning steps including ngram concatenation
# Add cleaned text column with removed stop words
emu$text_clean <- emu$text_clean |>
  str_remove_all(find_meta_stopwords(emu)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice", 
                      "space", "spatial", "spaces", "plan", "public", "development"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning")))

# Unnest words and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word))  # lemmatise words
```

>>>>

meta_sw <- find_meta_stopwords(emu)
emu_sw <- urbanism_stopwords(
    add_stopwords = c("emu", "european post[\\-]?(graduate)?[\\s]?master[s]? in urbanism",
                      "tu delft", "ku leuven", "upc barcelona", "iuav venice"))
thesis_sw <- thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "figure", "ning"))
anonymisation_sw <- c("EMAIL_REMOVED", "AUTHOR_REMOVED", "FIRST_NAME_REMOVED", "LAST_NAME_REMOVED") |>
  paste(collapse = "|")
custom_sw <- c("space[s]?", "spatial", "plan", "(plann)\\w{0,}", "public", "development",
               "design", "process[es]?", "project[s]?", "figure[s]?", "map[s]?", "strateg(y|ies)", "intervention[s]?",
               "create", "exist", "analys(i|e)s") |>
  (\(.) paste0("\\b", ., "\\b"))() |> 
  paste(collapse = "|")

# Add cleaned text column
emu$text_clean <- emu$text_raw |> 
  # Remove text included with anonymisation
  str_remove_all(anonymisation_sw) |>
  # Remove white spaces and punctuation, and change text to lower-case
  clean_basic() |>
  # Remove title, subtitle and full title
  str_remove_all(meta_sw) |> 
  # Remove dataset-specific words
  str_remove_all(emu_sw) |>
  # Remove thesis-specific words
  str_remove_all(thesis_sw)

# Concatenate ngrams
emu$text_clean <- emu |> 
  c_ngrams(n_max = 3, text_col = "text_clean",
           title_col = "title", min_freq = 20, lemma = TRUE)

# Words that were not included in ngrams are safe to remove now
emu$text_clean <- emu$text_clean |> 
  str_remove_all(custom_sw)

# # Get all concatenated ngrams
# unique(unlist(str_match_all(emu$text_clean, "[A-Za-z]+(?:_[A-Za-z]+)+")[1]))

# # Check if the word "space" was removed
# unique(unlist(str_match_all(emu$text_clean, "\\bspace\\b")))
# unique(unlist(str_match_all(emu$text_clean, "space(?:_[A-Za-z]+)+")))

```{r tokenise}

# TODO Replace title column with ID column

# Unnest tokens and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word)) |>  # lemmatise words
  filter(nchar(word) >= 3)  # keep only words that are at least three letters long

# # Check if concatenated ngrams are retained
# unlist(str_match_all(emu_words$word, "[A-Za-z]+(?:_[A-Za-z]+)+"))
```
